The Concurrent Calculi Formalisation Benchmark

### 2023-10-12 paper/paper.tex
Fix a few small mistakes.

To achieve our design goal \ref{item:goal-comperison-accessibility},
we have designed our challenge problems to exercise the three aspects (linearity, scope extrusion, coinduction) independently, and they can be solved individually and in any order.
We have designed each problem to be small and easy to understand with basic knowledge of textbook concurrency theory, process calculi and type theory.  The process calculus used in each challenge
focuses on the features we want to exercise, and we have omitted all constructs
(such as choices) that would complicate the mechanisation without bringing tangible
benefits and insights.  (Re-adding the omitted constructs if of course possible, but we leave
such extensions as a possibility for future benchmark challenge.)

@@

Linearity is of course interesting in many other subfields of programming languages, and we have thus chosen to base our challenge on a  session type system primarily due to the common use of session types in concurrency theory.

Inspired by Vasconcelos~\cite{Vasconcelos2012}, we use a syntax where
restriction binds two variables. This presentation makes the duality
of the two names obvious in the type system.

We have simple notion of well-formedness for our challenge problem,
and does not for instance consider deadlocked processes. While more
sophisticated notions of well-formedness are also interesting, the
proofs of these properties are more complicated and would thus make
the challenge problem more difficult and less focused on the linear
aspects of the system.

>>>>

To achieve our design goal \ref{item:goal-comperison-accessibility},
we have designed our challenge problems to exercise the three aspects (linearity, scope extrusion, coinduction) independently, and they can be solved individually and in any order.
We have designed each problem to be small and easy to understand with basic knowledge of textbook concurrency theory, process calculi and type theory.  The process calculus used in each challenge
focuses on the features we want to exercise, and we have omitted all constructs
(such as choices) that would complicate the mechanisation without bringing tangible
benefits and insights.  (Adding the omitted constructs is of course possible, but we leave
such extensions as a possibility for a future benchmark challenge.)

@@

Linearity is of course interesting in many other subfields of programming languages, but we have chosen to base our challenge on a session type system primarily due to the common use of session types in concurrency theory.

Inspired by Vasconcelos~\cite{Vasconcelos2012}, we use a syntax where
restriction binds two names. This presentation makes the duality
of the two names obvious in the type system.

We have chosen a simple notion of well-formedness for our challenge problem,
and do not for instance consider deadlocked processes. While more
sophisticated notions of well-formedness are also interesting, the
proofs of these properties are more complicated and would thus make
the challenge problem more difficult and less focused on the linear
aspects of the system.
